Program Mutation is Just Program Transformation: \\ A Universal Approach to Mutant Generation

### 2023-03-22 paper/main.tex
tce note
redacted cite for um paper

@@

>>>>

Our approach also makes introducing advanced techniques such as
Trivial Compiler Equivalence (TCE) into a mutation workflow easy.
While we support TCE for some languages inside the tool, a user can
always write a simple script to check...

@@

The approach reported in this paper was briefly presented in part in a
tool paper (citation redacted for blinding purposes) that introduced
the idea of using regular expressions to generate mutants for multiple
languages, and provided an evaluation against PIT for a single toy
Java program.  The present paper provides the full idea and context,
provides empirical data for universal mutant generation on real world
programs over four languages,
and introduces the idea of using parser-parser combinators to improve
on regular expression-based generation.
